\Large \bf New Static Analysis Techniques to Detect Entropy Failure Vulnerabilities

### 2018-12-13 paper/paper.tex
updates
taint analysis

@@

Taint analysis is a standard program analysis technique, typically used to detect security vulnerabilities in either a static or dynamic manner. 
We restrict our focus to the static variant. Taint analysis takes as input an initial assignment of some taint sets $\{\tau_i\}$ to 
a sources (program variables) $\{\sigma_i\}$, as well as a list of sinks $\{\zeta_i\}$ (function definitions). 
Taint is propagated through program statements using the semantics of the programming language;
for example, a variable $z = x + y$ will be assigned taint set $\tau_x \cup \tau_y$. The taint analysis outputs the taint set for each invocation
of the sinks $\{\zeta_i\}$.

@@

\bibliographystyle{alpha}
\bibliography{refs}

>>>>

\begin{abstract}
 Test abstract
\end{abstract}

@@

Taint analysis is a standard program analysis technique, typically used to detect security vulnerabilities in either a static or dynamic manner. 
We restrict our focus to the static variant. We define a taint analysis algorithm as follows:

\begin{itemize}
    \item $\Gamma \gets \mathsf{Taint}_{S,L}(\phi, T, \Sigma, Z, P)$: Takes as input an initial assignment $\phi$ of some taint sets $T = \{\tau_i\}$ to 
    a set of sources $\Sigma = \{\sigma_i\}$, and an input program $P$. Outputs an 
    assignment $\Gamma$ of statements $s_i$ in the program $P$ to taint sets $\rho_i$ according to the taint propagation semantics $S$ for programming
    language $L$.
\end{itemize}

@@

{\normalsize \bibliographystyle{acm}
\bibliography{refs}}
